---
title: "p8105_hw6_cj2493"
author: "Courtney Johnson"
date: "November 20, 2018"
output: github_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)
library(tidyverse)
library(modelr)
library(mgcv)
library(purrr)
```

## Problem 1

Read in the homicide data:

```{r, read_hom}
homicides = read_csv("https://raw.githubusercontent.com/washingtonpost/data-homicides/master/homicide-data.csv") 
```

Clean data accordingly: create city_state variable, a binary variable denoting whether the case was solved, omit cities who don't report victim race or were the product of a data entry mistake, modify victim race to white and non-white, and make sure victim_age is numeric.

```{r, hom_clean}
homicides = homicides %>%
  janitor::clean_names() %>%
  mutate(city_state = str_c(city, ", ", state),
         victim_age = as.numeric(victim_age),
         victim_race = ifelse(victim_race == "White", c("white"), c("non_white")),
         resolved = as.numeric(disposition == "Closed by arrest")) %>%
  filter(city_state != "Dallas, TX" & city_state != "Phoenix, AZ" & city_state != "Kansas City, MO" & city_state != "Tulsa, AL") %>%
  mutate(victim_sex = factor(victim_sex, levels = c("Male", "Female")),
         victim_race = fct_relevel(victim_race, "white"))
```

For Baltimore, MD, use glm function to fit a logistic regression with resolved vs unresolved as outcome and victim age, sex and race as predictors


```{r, baltimore_glm}
baltimore_hom = homicides %>%
  filter(city_state == "Baltimore, MD") 
 

balt_logistic = baltimore_hom %>%
  glm(resolved ~ victim_age + victim_sex + victim_race, data = ., family = binomial()) %>%
  broom::tidy()
```

Run glm for each of the cities in the dataset and extract the adjusted OR and CI for solving homicides comparing white and non-white victims.

```{r, pipe_glm}
nest_glm = homicides %>%
  group_by(city_state) %>%
  nest() %>%
  mutate(models = map(data, ~glm(resolved ~ victim_age + victim_sex + victim_race, data = ., family = binomial())),
         models = map(models, broom::tidy)) %>%
  select(-data) %>%
  unnest()
```

## Problem 2

Load and clean birthweight data

```{r, read_birth}
birthweight = read_csv("./data/birthweight.csv")
birthweight = birthweight %>%
  mutate(babysex = as.factor(babysex),
         frace = as.factor(frace),
         malform = as.factor(malform),
         mrace = as.factor(mrace))
birthweight[!complete.cases(birthweight), ] 
```

There are 0 observations, so this shows that there are no missing values in the data set. 


Propose a regression model for birthweight:

```{r, bwt_model}
bwt_model_1 = birthweight %>%
  lm(bwt ~ mrace + fincome + malform + momage + pnumlbw + smoken, data = .) %>%
  broom::tidy() 
```

